Classical Planning Algorithms ¡ on the Atari Video Games: Preliminary Results

### 2014-10-31 workshop-paper/performance_table.tex
Table updated

\begin{table*}
\addtolength{\tabcolsep}{-2pt}
{\scriptsize
\begin{tabular}{@{}l|rr|rrr|rrr|rrr|rrr@{}}
%% table header
\hline\\[-3ex]
\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Random} & \multicolumn{3}{c|}{BrFS}& \multicolumn{3}{c|}{IW1}& \multicolumn{3}{c|}{BFS}& \multicolumn{3}{c}{UCT} \\[.2ex]
\hline\\[-3ex]
%% table body
\multicolumn{1}{c}{Game}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Std Dev}  & \multicolumn{1}{c}{Time} & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} & \multicolumn{1}{|c}{Time} & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev}  & \multicolumn{1}{|c}{Time} & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev}  & \multicolumn{1}{|c}{Time} & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} \\[.2ex]
\hline\\[-3ex]
asterix         & 210   & 54.77     & 32.24 & 3900  & 5538.95   & 17.08 & 119000        & 4987.48   & 0.95  & 56320       & 4757.84   & 10.82 & \textbf{296300} & 6657.7    \\
beam\_rider     & 448.8 & 84.64     & 43.48 & 519.2 & 179.81    & 6.02  & 3000          & 1150.22   & 0.92  & 3804        & 446.18    & 42.91 & \textbf{4320}   & 2175.26   \\
breakout        & 1     & 0.71      & 51.56 & 2     & 1.41      & 1.37  & 383.6         & 9.84      & 3.95  & 421.2       & 13.66     & 26.03 & \textbf{512.4}  & 193.97    \\
enduro          & 0     & 0         & 40.92 & 0.4   & 0.89      & 38.13 & \textbf{500}  & 0         & 13.12 & 292.8       & 6.18      & 32.14 & 306.8           & 8.14      \\
freeway         & 0     & 0         & 71.84 & 0     & 0         & 15.19 & \textbf{29.4} & 0.89      & 4.44  & 19.6        & 3.29      & 90.64 & 1               & 1.41      \\
pong            & -20.4 & 0.55      & 41.51 & -20.2 & 0.84      & 18.45 & 16.4          & 1.67      & 39.69 & \textbf{21} & 0         & 38.37 & \textbf{21}     & 0         \\
qbert           & 185   & 345.33    & 42.83 & 160   & 85.88     & 1.82  & 1545          & 1666.06   & 1.76  & 14725       & 7872.1    & 28.61 & \textbf{18730}  & 1127.69   \\
seaquest        & 192   & 38.99     & 40.01 & 200   & 14.14     & 14.72 & \textbf{4274} & 4206.81   & 1.59  & 4070        & 1939.55   & 26.16 & 3406            & 2402.47   \\
space\_invaders & 187   & 120.86    & 46.11 & 115   & 61.44     & 12.1  & \textbf{2670} & 637.3     & 2.25  & 1327        & 598.04    & 19.66 & 2634            & 375.66   
\end{tabular}
}

 \caption{\small
   Random, BrFS, IW1, BFS, UCT performance over 5 runs, with
   seeds 0 to 4. \textit{Time} is the action selection average
   computation time in seconds, \textit{Avg. Score} is the average score, and
   \textit{Std Dev} is the standard deviation.  Numbers in bold show best performer in terms of average score.}
\label{performance}

>>>>

\begin{table*}
\addtolength{\tabcolsep}{-2pt}
{\scriptsize
\begin{tabular}{@{}l|rr|rrr|rrr|rrr|rrr@{}}
%% table header
\hline\\[-3ex]
\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Random} & \multicolumn{3}{c|}{BrFS}& \multicolumn{3}{c|}{IW1}& \multicolumn{3}{c|}{BFS}& \multicolumn{3}{c}{UCT} \\[.2ex]
\hline\\[-3ex]
%% table body
\multicolumn{1}{c}{Game}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Std Dev}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} &  \multicolumn{1}{c|}{Time}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} & \multicolumn{1}{c|}{Time}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} & \multicolumn{1}{c|}{Time}  & \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Std Dev} & \multicolumn{1}{c}{Time}\\[.2ex]
\hline\\[-3ex]
asterix         & 210    & 54.77     & 3900  & 5538.95   & 32.24 & 119000        & 4987.48   & 17.08 & 56320       & 4757.84   & 0.95  & \textbf{296300 (290700)} & 6657.7    & 10.82 \\
beam\_rider     & 448.8  & 84.64     & 519.2 & 179.81    & 43.48 & 3000          & 1150.22   & 6.02  & 3804        & 446.18    & 0.92  & \textbf{4320 (6624)}     & 2175.26   & 42.91 \\
breakout        & 1      & 0.71      & 2     & 1.41      & 51.56 & 383.6         & 9.84      & 1.37  & 421.2       & 13.66     & 3.95  & \textbf{512.4 (364)}     & 193.97    & 26.03 \\
enduro          & 0      & 0         & 0.4   & 0.89      & 40.92 & \textbf{500}  & 0         & 38.13 & 292.8       & 6.18      & 13.12 & 306.8 (286)              & 8.14      & 32.14 \\
freeway         & 0      & 0         & 0     & 0         & 71.84 & \textbf{29.4} & 0.89      & 15.19 & 19.6        & 3.29      & 4.44  & 1 (0)                    & 1.41      & 90.64 \\
pong            & -20.4  & 0.55      & -20.2 & 0.84      & 41.51 & 16.4          & 1.67      & 18.45 & \textbf{21} & 0         & 39.69 & \textbf{21 (21)}         & 0         & 38.37 \\
qbert           & 185    & 345.33    & 160   & 85.88     & 42.83 & 1545          & 1666.06   & 1.82  & 14725       & 7872.1    & 1.76  & \textbf{18730 (17343)}   & 1127.69   & 28.61 \\
seaquest        & 192    & 38.99     & 200   & 14.14     & 40.01 & \textbf{4274} & 4206.81   & 14.72 & 4070        & 1939.55   & 1.59  & 3406 (5132)              & 2402.47   & 26.16 \\
space\_invaders & 187    & 120.86    & 115   & 61.44     & 46.11 & \textbf{2670} & 637.3     & 12.1  & 1327        & 598.04    & 2.25  & 2634 (2718)              & 375.66    & 19.66
\end{tabular}
}

 \caption{\small Random, BrFS, IW1, BFS, UCT performance over 5 runs,
   with seeds 0 to 4, and maximum duration of 18.000
   frames. \textit{Time} is the action selection average computation
   time in seconds, \textit{Avg. Score} is the average score achieved,
   and \textit{Std Dev} is the standard deviation.  UCT performance
   reported in \cite{bellemare:jair} is shown in parenthesis. Numbers
   in bold show best performer in terms of average score.}
\label{performance}
